Multi-level modelling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-28 3-Introduction.tex

Model federation is a multi model management approach based on the use of virtual models and loosely coupled links. The models in a federation remain autonomous and represented in their original technological spaces whereas virtual models (also called conceptual models) and links serve as control components used to present different views to the users and maintain synchronization. 
Our solution is based on the model federation infrastructure, namely, the use of virtual models and links. Concretely, we use OpenFlexo and its internal Flexo Modeling Language (\FML), a language to create, link and manage virtual models, in order to solve the MULTI process challenge while the federation aspect is used solely as a means to provide tooling for the resulting process language. Our solution, which is fully implemented and executable, meets all the requirements. 
%Links among models can be within a same level of abstraction or across levels of abstractions which gives,

>>>>

Model federation is a multi model management approach based on the use of virtual models and loosely coupled links. The models in a federation remain autonomous and represented in their original technological spaces whereas virtual models (also called conceptual models) and links serve as control components used to present different views to the users and maintain synchronization. 
Our solution is based on the model federation infrastructure, namely, the use of virtual models and links. Concretely, we use OpenFlexo and its internal Flexo Modeling Language (\FML), a language to create, link and manage virtual models, in order to solve the MULTI process challenge while the federation aspect is used solely so as to provide tooling for the resulting process language. Our solution, which is fully implemented and executable, meets all the requirements.

%Links among models can be within a same level of abstraction or across levels of abstractions which gives,

### 2021-05-28 6-ModelPresentation.tex

Figure \ref{fig:BaseMetamodel} represents this base metamodel with a UML-like formalism, well adapted to represent object-oriented FML concepts and their instances. Base conceptual element is called a \textit{FlexoConcept} in FML language, and is similar to the concept of class in object-oriented modeling. The UML representation of class is used to represent a \textit{FlexoConcept}, while cardinalities are shown using the UML-like classical rules. 
In the diagram, we choose to represent the role associated with the \textit{FlexoConcept} in the class square and the role type is referenced by the arrow in front of the role name.

>>>>

Figure \ref{fig:BaseMetamodel} represents this base metamodel with a \UML-like formalism, well adapted to represent object-oriented \FML concepts and their instances. Base conceptual element is called a \textit{FlexoConcept} in \FML language, and is similar to the concept of class in object-oriented modeling. The \UML representation of class is used to represent a \textit{FlexoConcept}, while cardinalities are shown using the \UML-like classical rules. 
In the diagram, we choose to represent the role associated with the \textit{FlexoConcept} in the class square and the role type is referenced by the arrow in front of the role name.
